NumPy---Array Computation for Python

### 2019-12-20 paper.tex
Minor changes

% developed best practices, version control, unit testing, code review,
% runable documentation, \cite{millman2014developing}
% Travis steps back, no focused community effort until grant

To coordinate work as a global community, to ensure accuracy of
computed results, and to allow modification without breakage, the
NumPy community pioneered best software engineering practices in the
scientific Python community.  For example, NumPy early on adopted
distributed revision control, unit testing, continuous integration,
code review, standardized executable documentation, ...

@@

% built up technical debt, from a legacy of code from two projects
% and a lack of fulltime attention left ...

@@

% From grant text/summary on Sloan website:
%
% to remove the technical debt and set in place standards and
% architecture to encourage more sustainable development

% In 2014, NumPy received its
% first large grants from the Moore and Sloan foundations, totaling 1.3M
% dollars.  This allowed for hiring several full time programmers and,
% with the support of community members, mobilized a project that had
% become stagnant for the several years prior.

@@

% how much do we say about who these developers are and
% lessons learned?

@@

% Tidelift, ...
% https://tidelift.com/subscription/pkg/pypi-numpy
% $10,000 over 24 months according to
% https://mail.python.org/pipermail/numpy-discussion/2018-September/078736.html

>>>>

To coordinate work as a global community, to ensure accuracy of computed
results, and to allow modification without breakage, the NumPy community
pioneered best software engineering practices in the scientific Python
community  \cite{millman2014developing}.
For example, NumPy early on adopted distributed revision control, unit testing,
continuous integration, code review, and standardized executable documentation.

@@

@@

@@

@@
